---
title: "Memory Facial Threat"
author: "Graham Albert"
date: "June 9, 2019"
output: html_document
---


###To load required packarges
```{r}
require(curl) 
```
######loading data
#####for more advanced rotation.
```{r}
require(dplyr)
```
####for data manipulation.
```{r}
require(yaml)
require(stringi)
```
####for correlation plot depiction.
```{r}
require(gplots)
require(ggplot2)
require(gridExtra)
require(moments)
```

###To load glmm.
```{r}
require(lme4)
require(AICcmodavg)
require(MuMIn)
require(r2glmm)
```
####T
```{r}
require(RColorBrewer) # needed for some extra colours in one of the graphs
require(lmerTest)# to get p-value estimations that are not part of the standard lme4 packages
```


####To load my data set for the mating motivation scale into the  R work space.
```{r}
f <- curl("https://raw.githubusercontent.com/GrahamAlbert/Voice_Health_Revised/master/Study_3_Male_Dominance_Ratings_Long.csv")
VHS3DR<- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(VHS3DR)
```

####To determine variable names of the data set.
```{r}
names(VHS3DR)[1]<-"ID"
names(VHS3DR)

```

####Lets obtain some summary statistics.
```{r}
summary(VHS3DR)
dim(VHS3DR)
View(VHS3DR)
```

####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####These are: ID, participant sex, and speaker ID.
####The fixed effects in this analysis will be  health status.
```{r}
require(dplyr)
VHS3DR_factored = mutate(VHS3DR,ID = as.factor(VHS3DR$ID), Manipulation_Type = as.factor(VHS3DR$Manipulation_Type), SPEAKER_ID = as.factor(VHS3DR$SPEAKER_ID))
View(VHS3DR_factored)
```

####Lets determine if we effectively factors the variables of interested.
###We will determine the number of levels for each factor.
```{r}
nlevels(VHS3DR_factored$ID)
nlevels(VHS3DR_factored$Manipulation_Type)
nlevels(VHS3DR_factored$SPEAKER_ID)
```

####Lets look at the distribution of our dependents variables by plotting histrograms
```{r}
require(psych)
hist(VHS3DR_factored$Physical_Dominance_F0)
hist(VHS3DR_factored$Physical_Dominance_VTL)
hist(VHS3DR_factored$Social_Dominance_F0)
hist(VHS3DR_factored$Social_Dominance_VTL)
describe(VHS3DR_factored[c(4:7)])
```


####To recode recall and encoding so that the reference category changes.
```{R}
VHS3DR_factored$Manipulation_Type = factor(VHS3DR_factored$Manipulation_Type,
                             levels = c(0,1),
                             labels = c("Masculinized_F0_VTL", "Feminized_F0_VTL"))
table(VHS3DR_factored$Manipulation_Type)
```

####Lets save this data.
```{r}
VHS3DR_Master= VHS3DR_factored
summary(VHS3DR_Master)
write.csv(VHS3DR_Master,"C:\\Users\\graha\\Documents\\Github\\Voice_Health_Revised\\VHS3DR_Master", row.names = FALSE)
```







####The dependent variable is listener's physical dominance ratings


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is F0 manipulation.

```{r}
require(lme4)
PDFO <- lmer(Physical_Dominance_F0~Manipulation_Type+(1|ID)+(1|SPEAKER_ID),REML = FALSE,
           data=VHS3DR_Master)
summary(PDFO)
```


###To compute adjusted R squared.
```{r}
require(MuMIn)
r.squaredGLMM(PDFO)
```
####Let's check our multiple regression assumption set for model..
####First, we can check for homoscedasticity . 
```{r}
plot(fitted(PDFO), resid(PDFO, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(PDFO)) 
qqline(resid(PDFO), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(PDFO)
confint(PDFO)
```



####Let's generate the AIC for the 8 models.
```{r}
require(AICcmodavg)
print(aictab(list(PDFO), c("PDFO"), LL = FALSE))
```





####The dependent variable is listener's physical dominance ratings


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is apparent VTL manipulation.









#Now lets add the categorical fixed of health status (healthy/unhealth).
```{r}
require(lme4)
PDVTL <- lmer(Physical_Dominance_VTL~Manipulation_Type+(1|ID)+(1|SPEAKER_ID),REML = FALSE,
           data=VHS3DR_Master)
summary(PDVTL)
```

###To compute adjusted R squared.
```{r}
require(MuMIn)
r.squaredGLMM(PDVTL)
```
####Let's check our multiple regression assumption set for model 10.
####First, we can check for homoscedasticity by comparing residuals to the fitted items. 
```{r}
plot(fitted(PDVTL), resid(PDVTL, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(PDVTL)) 
qqline(resid(PDVTL), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(PDVTL)
confint(PDVTL)
```



####Let's generate the AIC for the 8 models.
```{r}
require(AICcmodavg)
print(aictab(list(PDVTL), c("PDVTL"), LL = FALSE))
```




####The dependent variable is listener's social dominance


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is apparent F0 manipulation.




```{r}
require(lme4)
SDFO <- lmer(Social_Dominance_F0~Manipulation_Type+(1|ID)+(1|SPEAKER_ID),REML=FALSE,
           data=VHS3DR_Master)
summary(SDFO)
```

###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(SDFO)
```
####Let's check our multiple regression assumption set for model.
####First, we can check for homoscedasticity . 
```{r}
plot(fitted(SDFO), resid(SDFO, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(SDFO)) 
qqline(resid(SDFO), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(SDFO)
confint(SDFO)
```



####Let's generate the AIC for the 8 models.
```{r}
require(AICcmodavg)
print(aictab(list(SDFO), c("SDFO"), LL = FALSE))
```






####The dependent variable is listener's social dominance


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is apparent VTL manipulation.


```{r}
require(lme4)
SDVTL <- lmer(Social_Dominance_VTL~Manipulation_Type+(1|ID)+(1|SPEAKER_ID),REML = FALSE,
           data=VHS3DR_Master)
summary(SDVTL)
```

###To compute adjusted R squared.
```{r}
require(MuMIn)
r.squaredGLMM(SDVTL)
```
####Let's check our multiple regression assumption set for model 10.
####First, we can check for homoscedasticity by comparing residuals to the fitted items. 
```{r}
plot(fitted(SDVTL), resid(SDVTL, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(SDVTL)) 
qqline(resid(SDVTL), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(SDVTL)
confint(SDVTL)
```



####Let's generate the AIC for the 8 models.
```{r}
require(AICcmodavg)
print(aictab(list(SDVTL), c("SDVTL"), LL = FALSE))
```





