---
title: "Study 1 Women's Attractiveness Ratings"
author: "Graham Albert"
date: "June 9, 2019"
output: html_document
---


###To load required packarges
```{r}
require(curl) 
```
######loading data
#####for more advanced rotation.
```{r}
require(dplyr)
```
####for data manipulation.
```{r}
require(yaml)
require(stringi)
```
####for correlation plot depiction.
```{r}
require(gplots)
require(ggplot2)
require(gridExtra)
require(moments)
```

###To load packaged for the mixed effects regressions.
```{r}
require(lme4)
require(AICcmodavg)
require(MuMIn)
require(r2glmm)
```
####More packages for the mixed effects regressions.
```{r}
require(RColorBrewer) # needed for some extra colours in one of the graphs
require(lmerTest)# to get p-value estimations that are not part of the standard lme4 packages
```


####To load my data set for the mating motivation scale into the  R work space.
```{r}
f <- curl("https://raw.githubusercontent.com/GrahamAlbert/Voice_Health_Revised/master/Study_1_Attractiveness_Based_Ratings_Long_MLM.csv")
VHS1AR<- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(VHS1AR)
```

####To determine variable names of the data set.
```{r}
names(VHS1AR)[1]<-"ID"
names(VHS1AR)

```

####Lets obtain some summary statistics.
```{r}
summary(VHS1AR)
dim(VHS1AR)
View(VHS1AR)
```

####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects are liststner ID and speaker ID.
####The fixed effects in this analysis will be  health status.
```{r}
require(dplyr)
VHS1AR_factored = mutate(VHS1AR,ID = as.factor(VHS1AR$ID), Health_Status = as.factor(VHS1AR$Health_Status), SPEAKER_ID = as.factor(VHS1AR$SPEAKER_ID))
View(VHS1AR_factored)
```

####Lets determine if we effectively factors the variables of interested.
###We will determine the number of levels for each factor.
```{r}
nlevels(VHS1AR_factored$ID)
nlevels(VHS1AR_factored$Health_Status)
nlevels(VHS1AR_factored$SPEAKER_ID)
```

####Lets look at the distribution of our dependents variables by plotting histrograms
```{r}
require(psych)
hist(VHS1AR_factored$Long_term_attractivenes)
hist(VHS1AR_factored$Short_term_attractiveness)
describe(VHS1AR_factored[c(4:5)])
```


####To factor health status.
```{R}
VHS1AR_factored$Health_Status = factor(VHS1AR_factored$Health_Status,
                             levels = c(0,1),
                             labels = c("Unhealthy", "Healthy"))
table(VHS1AR_factored$Health_Status)
```
####The dependent variable is long-term attractiveness ratings

####Lets enter the random effects of participant ID and speaker ID as well as the fixed effect 
#####Lets add the fixed effects of health statue (healthy/unhealthy).
```{r}
require(lme4)
LTAMODEL <- lmer(Long_term_attractiveness ~ Health_Status+(1|ID)+(1|SPEAKER_ID),REML = FALSE,
           data=VHS1AR_factored)
summary(LTAMODEL)
```

###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(LTAMODEL)
```
####Let's check our multiple regression assumption set for the model.
####First, we can check for homoscedasticity by comparing residuals to the fitted items. 
```{r}
plot(fitted(LTAMODEL), resid(LTAMODEL, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(LTAMODEL)) 
qqline(resid(LTAMODEL), col = "red")
```

###To generate the fixed effects table for the models .
```{r}
fixef(LTAMODEL)
```



####Let's generate the AIC for the model.
```{r}
require(AICcmodavg)
print(aictab(list(LTAMODEL), c("LTAMODEL"), LL = FALSE))
```

####To generate confidence interval.
```{r}
confint(LTAMODEL)
```



####Dependent variabe is short term attractiveness rating.



#####Lets add the random effects of listener ID and speaker ID.
#####Lets add the fixed effects of health statue (healthy/unhealthy).
```{r}
require(lme4)
STAMODEL <- lmer(Short_term_attractiveness ~ Health_Status+(1|ID)+(1|SPEAKER_ID),REML = FALSE,
           data=VHS1AR_factored)
summary(STAMODEL)
```


####To generate confidence interval.
```{r}
confint(STAMODEL)
```


###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(STAMODEL)
```




####Let's check our multiple regression assumption set for the model.
####First, we can check for homoscedasticity by comparing residuals to the fitted items. 
```{r}
plot(fitted(STAMODEL), resid(STAMODEL, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(STAMODEL)) 
qqline(resid(STAMODEL), col = "red")
```

###To generate the fixed effects table for the model .
```{r}
fixef(STAMODEL)
```



####Let's generate the AIC for the model.
```{r}
require(AICcmodavg)
print(aictab(list(STAMODEL), c("STAMODEL"), LL = FALSE))
```








