---
title: "Memory Facial Threat"
author: "Graham Albert"
date: "June 9, 2019"
output: html_document
---


###To load required packarges
```{r}
require(curl) 
```
######loading data
#####for more advanced rotation.
```{r}
require(dplyr)
```
####for data manipulation.
```{r}
require(yaml)
require(stringi)
```
####for correlation plot depiction.
```{r}
require(gplots)
require(ggplot2)
require(gridExtra)
require(moments)
```

###To load in the packages for conducting the mixed effects models.
```{r}
require(lme4)
require(AICcmodavg)
require(MuMIn)
require(r2glmm)
```
###To load in the packages for conducting the mixed effects models.
```{r}
require(RColorBrewer) # needed for some extra colours in one of the graphs
require(lmerTest)# to get p-value estimations that are not part of the standard lme4 packages
```


####To load my data set for the mating motivation scale into the  R work space.
```{r}
f <- curl("https://raw.githubusercontent.com/GrahamAlbert/Voice_Health_Revised/master/Study_1_Health_Based_Ratings_Long_MLM.csv")
VHS1HR<- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(VHS1HR)
```

####To determine variable names of the data set.
```{r}
names(VHS1HR)[1]<-"ID"
names(VHS1HR)

```

####Lets obtain some summary statistics.
```{r}
summary(VHS1HR)
dim(VHS1HR)
View(VHS1HR)
```

####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####These are: ID, participant sex, and speaker ID.
####The fixed effects in this analysis will be  health status.
```{r}
require(dplyr)
VHS1HR_factored = mutate(VHS1HR,ID = as.factor(VHS1HR$ID), Health_Status = as.factor(VHS1HR$Health_Status), SPEAKER_ID = as.factor(VHS1HR$SPEAKER_ID))
View(VHS1HR_factored)
```

####Lets determine if we effectively factors the variables of interested.
###We will determine the number of levels for each factor.
```{r}
nlevels(VHS1HR_factored$ID)
nlevels(VHS1HR_factored$Health_Status)
nlevels(VHS1HR_factored$SPEAKER_ID)
```



####To recode recall and encoding so that the reference category changes.
```{R}
VHS1HR_factored$Health_Status = factor(VHS1HR_factored$Health_Status,
                             levels = c(0,1),
                             labels = c("Unhealthy", "Healthy"))
table(VHS1HR_factored$Health_Status)
```

####Lets save this data.
```{r}
VHS1HR_MASTER= VHS1HR_factored
summary(VHS1HR_MASTER)
write.csv(VHS1HR_MASTER,"C:\\Users\\graha\\Documents\\Github\\Voice_Health_Revised\\VHS1HR_MASTER", row.names = FALSE)
```





####The dependent variable is listener's health ratings.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis will be  health status (health/unhealthy)



#####Lets open LME4.
```{r}
require(lme4)
HEALTLHRATINGMODEL <- lmer(Health_Rating ~ Health_Status+(1|ID)+(1|SPEAKER_ID),REML = FALSE,
           data=VHS1HR_MASTER)
summary(HEALTLHRATINGMODEL)
```

###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(HEALTLHRATINGMODEL)
```
####Let's check our multiple regression assumption set for model 10.
####First, we can check for homoscedasticity by comparing residuals to the fitted items. 
```{r}
plot(fitted(HEALTLHRATINGMODEL), resid(HEALTLHRATINGMODEL, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(HEALTLHRATINGMODEL)) 
qqline(resid(HEALTLHRATINGMODEL), col = "red")
```

###To generate the fixed effects table for the models .
```{r}
fixef(HEALTLHRATINGMODEL)
```
####To conmpute confidence intervals for the estimate.
```{r}
confint(HEALTLHRATINGMODEL)
```


####Let's generate the AIC for the 8 models.
```{r}
require(AICcmodavg)
print(aictab(list(HEALTLHRATINGMODEL), c("HEALTLHRATINGMODEL"), LL = FALSE))
```

####The dependent variable is listener's disease likelihood ratings.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis will be  health status (health/unhealthy)


#Now lets add the categorical fixed of health status (healthy/unhealth).
```{r}
require(lme4)
DISEASELIKELIHOODMODEL <- lmer(Disease_Likelihood_Rating ~ Health_Status+(1|ID)+(1|SPEAKER_ID),REML = FALSE,
           data=VHS1HR_MASTER)
summary(DISEASELIKELIHOODMODEL)
```


###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(DISEASELIKELIHOODMODEL)
```
####Let's check our multiple regression assumption set for model.
####First, we can check for homoscedasticity by comparing residuals to the fitted items. 
```{r}
plot(fitted(DISEASELIKELIHOODMODEL), resid(DISEASELIKELIHOODMODEL, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(DISEASELIKELIHOODMODEL)) 
qqline(resid(DISEASELIKELIHOODMODEL), col = "red")
```

###To generate the fixed effects table for the models .
```{r}
fixef(DISEASELIKELIHOODMODEL)
```



####Let's generate the AIC for the  model.
```{r}
require(AICcmodavg)
print(aictab(list(DISEASELIKELIHOODMODEL), c("DISEASELIKELIHOODMODEL"), LL = FALSE))
```


####To conmpute confidence intervals for the estimate.
```{r}
confint(DISEASELIKELIHOODMODEL)
```


####The dependent variable is listener's illness frequency.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis will be  health status (health/unhealthy)


```{r}
require(lme4)
ILLNESSFREQUENCYMODEL<- lmer(Illness_Frequency_Rating ~ Health_Status+(1|ID)+(1|SPEAKER_ID),REML=FALSE,
           data=VHS1HR_MASTER)
summary(ILLNESSFREQUENCYMODEL)
```

###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(ILLNESSFREQUENCYMODEL)
```
####Let's check our multiple regression assumption  for the model.
####First, we can check for homoscedasticity by comparing residuals to the fitted items. 
```{r}
plot(fitted(ILLNESSFREQUENCYMODEL), resid(ILLNESSFREQUENCYMODEL, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residual. 
```{r}
qqnorm(resid(ILLNESSFREQUENCYMODEL)) 
qqline(resid(ILLNESSFREQUENCYMODEL), col = "red")

```

###To generate the fixed effects table for the model .
```{r}
fixef(ILLNESSFREQUENCYMODEL)
```



####Let's generate the AIC for the model.
```{r}
require(AICcmodavg)
print(aictab(list(ILLNESSFREQUENCYMODEL), c("ILLNESSFREQUENCYMODEL"), LL = FALSE))
```

###To generate the confidence intervals for the model.
```{r}
confint(ILLNESSFREQUENCYMODEL)
```




####The dependent variable is listener's symptom severity ratings.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis will be  health status (health/unhealthy)

```{r}
require(lme4)
SYMSEVMODEL<- lmer(Symptom_Severity_Ratings ~ Health_Status+(1|ID)+(1|SPEAKER_ID),REML=FALSE,
           data=VHS1HR_MASTER)
summary(SYMSEVMODEL)
```

###To compute adjusted R squared.
```{r}
require(MuMIn)
r.squaredGLMM(SYMSEVMODEL)
```
####Let's check our multiple regression assumption set for model.
####First, we can check for homoscedasticity by comparing residuals to the fitted items. 
```{r}
plot(fitted(SYMSEVMODEL), resid(SYMSEVMODEL, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(SYMSEVMODEL)) 
qqline(resid(SYMSEVMODEL), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(SYMSEVMODEL)
```



####Let's generate the AIC for the model.
```{r}
require(AICcmodavg)
print(aictab(list(SYMSEVMODEL), c("SYMSEVMODEL"), LL = FALSE))
```




###To generate the confidence interval for the modefl
```{r}
confint(SYMSEVMODEL)
```
