---
title: "F0 and VTL manipulation health ratings"
author: "Graham Albert"
date: "June 9, 2019"
output: html_document
---


###To load required packarges
```{r}
require(curl) 
```
######loading data
#####for more advanced rotation.
```{r}
require(dplyr)
```
####for data manipulation.
```{r}
require(yaml)
require(stringi)
```
####for correlation plot depiction.
```{r}
require(gplots)
require(ggplot2)
require(gridExtra)
require(moments)
```

###To load mixed effects models packages
```{r}
require(lme4)
require(AICcmodavg)
require(MuMIn)
require(r2glmm)
```
####To load more mixed effects models.
```{r}
require(RColorBrewer) # needed for some extra colours in one of the graphs
require(lmerTest)# to get p-value estimations that are not part of the standard lme4 packages
```


####To load my data set for the mating motivation scale into the  R work space.
```{r}
f <- curl("https://raw.githubusercontent.com/GrahamAlbert/Voice_Health_Revised/master/Study_3_Health_Based_Ratings_long_Corrected.csv")
VHS3HR<- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(VHS3HR)
```

####To determine variable names of the data set.
```{r}
names(VHS3HR)[1]<-"ID"
names(VHS3HR)
```

####Lets obtain some summary statistics.
```{r}
summary(VHS3HR)
dim(VHS3HR)
View(VHS3HR)
```

####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####These are: ID, participant sex, and speaker ID.
####The fixed effects in this analysis will be  health status.
```{r}
require(dplyr)
VHS3HR_factored = mutate(VHS3HR,ID = as.factor(VHS3HR$ID),ParticipantSex  = as.factor(VHS3HR$ParticipantSex), Manipulation_Type = as.factor(VHS3HR$Manipulation_Type), SPEAKER_ID = as.factor(VHS3HR$SPEAKER_ID))
View(VHS3HR_factored)
```

####Lets determine if we effectively factors the variables of interested.
###We will determine the number of levels for each factor.
```{r}
nlevels(VHS3HR_factored$ID)
nlevels(VHS3HR_factored$ParticipantSex)
nlevels(VHS3HR_factored$Manipulation_Type)
nlevels(VHS3HR_factored$SPEAKER_ID)
```

####Lets look at the distribution of our dependents variables by plotting histrograms
```{r}
require(psych)
hist(VHS3HR_factored$Health_Rating_F0)
hist(VHS3HR_factored$Health_Rating_VTL)
hist(VHS3HR_factored$Disease_Likelihood_Rating_F0)
hist(VHS3HR_factored$Disease_Likelihood_Rating_VTL)
hist(VHS3HR_factored$Illness_Frequency_F0)
hist(VHS3HR_factored$Illness_Frequency_VTL)
hist(VHS3HR_factored$Symptom_Severity_F0)
hist(VHS3HR_factored$Symptom_Severity_VTL)
describe(VHS3HR_factored[c(5:12)])
```


####To recode recall and encoding so that the reference category changes.
```{R}
VHS3HR_factored$ParticipantSex = factor(VHS3HR_factored$ParticipantSex,
                             levels = c(0,1),
                             labels = c("Male", "Female"))
table(VHS3HR_factored$ParticipantSex)
VHS3HR_factored$Manipulation_Type = factor(VHS3HR_factored$Manipulation_Type,
                             levels = c(0,1),
                             labels = c("Masculinized_F0_VTL", "Feminized_F0_VTL"))
table(VHS3HR_factored$Manipulation_Type)
```

####Lets save this data.
```{r}
VHS3HR_Master= VHS3HR_factored
summary(VHS3HR_Master)
write.csv(VHS3HR_Master,"C:\\Users\\graha\\Documents\\Github\\Voice_Health_Revised\\VHS3HR_Master", row.names = FALSE)
```





####The dependent variable is listener's health ratings.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is F0 manipulation.


```{r}
require(lme4)
HEALTHRATINGF0 <- lmer(Health_Rating_F0 ~ Manipulation_Type+(1|ID)+(1|SPEAKER_ID), REML=FALSE,
           data=VHS3HR_Master)
summary(HEALTHRATINGF0)
```

###To compute adjusted R squared.
```{r}
require(MuMIn)
r.squaredGLMM(HEALTHRATINGF0)
```
####Let's check our multiple regression assumption set for the model.
####First, we can check for homoscedasticity . 
```{r}
plot(fitted(HEALTHRATINGF0), resid(HEALTHRATINGF0, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(HEALTHRATINGF0)) 
qqline(resid(HEALTHRATINGF0), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(HEALTHRATINGF0)
confint(HEALTHRATINGF0)
```



####Let's generate the AIC for the model.
```{r}
require(AICcmodavg)
print(aictab(list(HEALTHRATINGF0), c("HEALTHRATINGF0"), LL = FALSE))
```


####The dependent variable is listener's health ratings.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is apparent VTL manipulation
.
```{r}
require(lme4)
HEALTHRATINGVTL <- lmer(Health_Rating_VTL ~ Manipulation_Type+(1|ID)+(1|SPEAKER_ID),
           data=VHS3HR_Master,REML=FALSE)
summary(HEALTHRATINGVTL)
```


###Lets get the confidence intervals for the model.
```{r}
confint(HEALTHRATINGVTL)
```

###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(HEALTHRATINGVTL)
```
####Let's check our multiple regression assumption set for the model.
####First, we can check for homoscedasticity . 
```{r}
plot(fitted(HEALTHRATINGVTL), resid(HEALTHRATINGVTL, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(HEALTHRATINGVTL)) 
qqline(resid(HEALTHRATINGVTL), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(HEALTHRATINGVTL)
confint(HEALTHRATINGVTL)
```
####Let's generate the AIC for the model.
```{r}
require(AICcmodavg)
print(aictab(list(HEALTHRATINGVTL), c("HEALTHRATINGVTL"), LL = FALSE))
```




####The dependent variable is listener's  diseaselikelihood ratings.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is F0 manipulation.




###Our dependent variable will be diseaselikelihood ratings assigned to the voices with the apparent F0 manipulation

```{r}
require(lme4)
options(scipen=999)
DISEASELIKEFO <- lmer(Disease_Likelihood_Rating_F0 ~ Manipulation_Type+(1|ID)+(1|SPEAKER_ID),REML=FALSE,
           data=VHS3HR_Master)
summary(DISEASELIKEFO)
```

###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(DISEASELIKEFO)
```
####Let's check our multiple regression assumption set for model.
####First, we can check for homoscedasticity . 
```{r}
plot(fitted(DISEASELIKEFO), resid(DISEASELIKEFO, type = "pearson"))
abline(0,0, col="red")
```

####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(DISEASELIKEFO)) 
qqline(resid(DISEASELIKEFO), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(DISEASELIKEFO)
confint(DISEASELIKEFO)
```



####Let's generate the AIC for the models.
```{r}
require(AICcmodavg)
print(aictab(list(DISEASELIKEFO), c("DISEASELIKEFO"), LL = FALSE))
```



####The dependent variable is listener's  diseaselikelihood ratings.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is apparent VTL manipulation.




#Now lets control of individuals speaker in our analysis to ensure that other acoustic characteristics do not affect our 
#manipulations.
```{r}
require(lme4)
DISEASELIKEVTL<- lmer(Disease_Likelihood_Rating_VTL ~ Manipulation_Type+(1|ID)+(1|SPEAKER_ID),REML=FALSE,
           data=VHS3HR_Master)
summary(DISEASELIKEVTL)
```

###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(DISEASELIKEVTL)
```
####Let's check our multiple regression assumption set for the model.
####First, we can check for homoscedasticity. 
```{r}
plot(fitted(DISEASELIKEVTL), resid(DISEASELIKEVTL, type = "pearson"))
abline(0,0, col="red")
```

####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(DISEASELIKEVTL)) 
qqline(resid(DISEASELIKEVTL), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(DISEASELIKEVTL)
confint(DISEASELIKEVTL)
```



####Let's generate the AIC for the 8 models.
```{r}
require(AICcmodavg)
print(aictab(list(DISEASELIKEVTL), c("DISEASELIKEVTL"), LL = FALSE))
```


####The dependent variable is listener's illness frequency ratings.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is FO manipulation.



#Now lets control of individuals speaker in our analysis to ensure that other acoustic characteristics do not affect our 
#manipulations.
```{r}
require(lme4)
ILLFREQFO<- lmer(Illness_Frequency_F0 ~ Manipulation_Type+(1|ID)+(1|SPEAKER_ID),REML=FALSE,
           data=VHS3HR_Master)
summary(ILLFREQFO)
```

###To compute adjusted R squared.
```{r}
require(MuMIn)
r.squaredGLMM(ILLFREQFO)
```
####Let's check our multiple regression assumption set for model.
####First, we can check for homoscedasticity . 
```{r}
plot(fitted(ILLFREQFO), resid(ILLFREQFO, type = "pearson"))
abline(0,0, col="red")
```

####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(ILLFREQFO)) 
qqline(resid(ILLFREQFO), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(ILLFREQFO)
confint(ILLFREQFO)
```



####Let's generate the AIC for the 8 models.
```{r}
require(AICcmodavg)
print(aictab(list(ILLFREQFO), c("ILLFREQFO"), LL = FALSE))
```









####The dependent variable is listener's illness frequency ratings.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is apparent VTL manipulation.


```{r}
require(lme4)
ILLFREQVTL <- lmer(Illness_Frequency_VTL ~ Manipulation_Type+(1|ID)+(1|SPEAKER_ID),REML=FALSE,
           data=VHS3HR_Master)
summary(ILLFREQVTL)
```

###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(ILLFREQVTL)
```
####Let's check our multiple regression assumption set for model.
####First, we can check for homoscedasticity. 
```{r}
plot(fitted(ILLFREQVTL), resid(ILLFREQVTL, type = "pearson"))
abline(0,0, col="red")
```

####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(ILLFREQVTL)) 
qqline(resid(ILLFREQVTL), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(ILLFREQVTL)
confint(ILLFREQVTL)
```



####Let's generate the AIC for the  model.
```{r}
require(AICcmodavg)
print(aictab(list(ILLFREQVTL), c("ILLFREQVTL"), LL = FALSE))
```



















####The dependent variable is listener's symptom severity.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is F0 manipulation.



####To conduct a mixed effects model in which symptom severity for voices with the F0 manipulation

```{r}
require(lme4)
SYMSEVFO <- lmer(Symptom_Severity_F0 ~ Manipulation_Type+(1|ID)+(1|SPEAKER_ID), REML = FALSE,
           data=VHS3HR_Master)
summary(SYMSEVFO)
```

###To compute adjusted R squared.
```{r}
require(MuMIn)
r.squaredGLMM(SYMSEVFO)
```
####Let's check our multiple regression assumption set for model 10.
####First, we can check for homoscedasticity by comparing residuals to the fitted items. 
```{r}
plot(fitted(SYMSEVFO), resid(SYMSEVFO, type = "pearson"))
abline(0,0, col="red")
```

####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(SYMSEVFO)) 
qqline(resid(SYMSEVFO), col = "red")
```

###To generate the fixed effects table for the models .
```{r}
fixef(SYMSEVFO)
confint(SYMSEVFO)
```



####Let's generate the AIC for the model.
```{r}
require(AICcmodavg)
print(aictab(list(SYMSEVFO), c("SYMSEVFO"), LL = FALSE))
```





####The dependent variable is listener's symptom severity.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is apparent VTL manipulation.



####To conduct a mixed effects model in which symptom severity for voices with the apparent VTL manipulation.
```{r}
require(lme4)
SYMSEVVTL <- lmer(Symptom_Severity_VTL ~ Manipulation_Type+(1|ID)+(1|SPEAKER_ID),
           data=VHS3HR_Master)
summary(SYMSEVVTL)
```

###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(SYMSEVVTL)
```
####Let's check our multiple regression assumption set for model.
####First, we can check for homoscedasticity. 
```{r}
plot(fitted(SYMSEVVTL), resid(SYMSEVVTL, type = "pearson"))
abline(0,0, col="red")
```

####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(SYMSEVVTL)) 
qqline(resid(SYMSEVVTL), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(SYMSEVVTL)
confint(SYMSEVVTL)
```



####Let's generate the AIC for the models.
```{r}
require(AICcmodavg)
print(aictab(list(SYMSEVVTL), c("SYMSEVVTL"), LL = FALSE))
```


