---
title: "Memory Facial Threat"
author: "Graham Albert"
date: "June 9, 2019"
output: html_document
---


###To load required packarges
```{r}
require(curl) 
```
######loading data
#####for more advanced rotation.
```{r}
require(dplyr)
```
####for data manipulation.
```{r}
require(yaml)
require(stringi)
```
####for correlation plot depiction.
```{r}
require(gplots)
require(ggplot2)
require(gridExtra)
require(moments)
```

###To load in the packages for conducting the mixed effects models.
```{r}
require(lme4)
require(AICcmodavg)
require(MuMIn)
require(r2glmm)
```
#### More packages for conducting mixed effects models
```{r}
require(RColorBrewer) # needed for some extra colours in one of the graphs
require(lmerTest)# to get p-value estimations that are not part of the standard lme4 packages
```


####To load my data set for the mating motivation scale into the  R work space.
```{r}
f <- curl("https://raw.githubusercontent.com/GrahamAlbert/Voice_Health_Revised/master/Study_1_Dominance_Rating_Long_MLM.csv")
VHS1DR<- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(VHS1DR)
```

####To determine variable names of the data set.
```{r}
names(VHS1DR)[1]<-"ID"
names(VHS1DR)

```

####Lets obtain some summary statistics.
```{r}
summary(VHS1DR)
dim(VHS1DR)
View(VHS1DR)
```

####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis will be  health status (health/unhealthy)

```{r}
require(dplyr)
VHS1DR_factored = mutate(VHS1DR,ID = as.factor(VHS1DR$ID), Health_Status = as.factor(VHS1DR$Health_Status), SPEAKER_ID = as.factor(VHS1DR$SPEAKER_ID))
View(VHS1DR_factored)
```

####Lets determine if we effectively factors the variables of interested.
###We will determine the number of levels for each factor.
```{r}
nlevels(VHS1DR_factored$ID)
nlevels(VHS1DR_factored$Health_Status)
nlevels(VHS1DR_factored$SPEAKER_ID)
```

####Lets look at the distribution of our dependents variables by plotting histrograms
```{r}
require(psych)
hist(VHS1DR_factored$Physical_Domaince)
hist(VHS1DR_factored$Social_Dmanice)
describe(VHS1DR_factored[c(4:5)])
```


####To factor health status.
```{R}
VHS1DR_factored$Health_Status = factor(VHS1DR_factored$Health_Status,
                             levels = c(0,1),
                             labels = c("Unhealthy", "Healthy"))
table(VHS1DR_factored$Health_Status)
```


####Lets save this data.
```{r}
VHS1DR_Master= VHS1DR_factored
summary(VHS1DR_Master)
```



####Lets open LME4.
####The dependent variable is physical dominance ratings

####Lets enter the random effects of participant ID and speaker ID as well as the fixed effect 
#####Lets add the fixed effects of health statue (healthy/unhealthy).
```{r}
require(lme4)
PDRMODEL <- lmer(Physical_Domaince ~ Health_Status+(1|ID)+(1|SPEAKER_ID),REML = FALSE,
           data=VHS1DR_Master)
summary(PDRMODEL)
```

###To compute adjusted R squared.
```{r}
require(MuMIn)
r.squaredGLMM(PDRMODEL)
```
####Let's check our multiple regression assumption set for model 10.
####First, we can check for homoscedasticity by comparing residuals to the fitted items. 
```{r}
plot(fitted(PDRMODEL), resid(PDRMODEL, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(PDRMODEL)) 
qqline(resid(PDRMODEL), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
confint(PDRMODEL)
```


###To generate confidence interval
```{r}
fixef(PDRMODEL)
```


####Let's generate the AIC for the  models.
```{r}
require(AICcmodavg)
print(aictab(list(PDRMODEL), c("PDRMODEL"), LL = FALSE))
```


###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(PDRMODEL)
```





####Lets open LME4.
####The dependent variable is social dominance ratings

####Lets enter the random effects of participant ID and speaker ID as well as the fixed effect 
#####Lets add the fixed effects of health statue (healthy/unhealthy).


#Now lets add the categorical fixed of health status (healthy/unhealth).
```{r}
require(lme4)
SDRMODEL <- lmer(Social_Dmanice ~ Health_Status+(1|ID)+(1|SPEAKER_ID),REML = FALSE,
           data=VHS1DR_Master)
summary(SDRMODEL)
```


###To generate the fixed effects table for the model .
```{r}
confint(SDRMODEL)
```



###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(SDRMODEL)
```



####Let's generate the AIC for the  models.
```{r}
require(AICcmodavg)
print(aictab(list(SDRMODEL), c("SDRMODEL"), LL = FALSE))
```


####Let's check our multiple regression assumption set for model 10.
####First, we can check for homoscedasticity by comparing residuals to the fitted items. 
```{r}
plot(fitted(SDRMODEL), resid(SDRMODEL, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(SDRMODEL)) 
qqline(resid(SDRMODEL), col = "red")

```
