---
title: "Study 2 Multiple Linear Regression Acoustic Parameters Health Measures"
author: "Graham Albert"
date: "2/25/2020"
output: html_document
---

####To load required packarges
```{r}
require(curl) 
```
######missing data
```{r}
require(mice)
```
#####for more advanced rotation.
```{r}
require(dplyr)
```
####for data manipulation.
```{r}
require(yaml)
require(stringi)
require(dplyr)
```
####for  plot depiction.
```{r}
require(gplots)
require(ggplot2)
require(gridExtra)
require(moments)
```

###obtaining variable parameters.
```{r}
require(psych)##for EFA, and descriiptivves
require(BaylorEdPsych)####for missing value analysis
```


####Now we will read in the wide data set and conduct Pearson correlations.
####To load my data set for the mating motivation scale into the  R work space.
```{r}
f <- curl("https://raw.githubusercontent.com/GrahamAlbert/Voice_Health_Revised/master/Study_2_Data_20200513.csv")
VHS12<- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
View(VHS12)
names(VHS12)
```

####To determine variable names of the data set.
```{r}
names(VHS12)[1]<-"ID"
names(VHS12)
```



####To obtain the descriptive statistics includinag the skewness and kurtosis values of the variables.
```{r}
require(psych)
norm = describe(VHS12[-c(1)])
View(norm)
```
####Lets start with the Reby and McComb measure of VTL.
```{r}
VHS12_2 <- VHS12[-c(2,5,6,9:11,14,15)]
View(VHS12_2)
```

####To screening for missing values.
####To write a funtion to check for missng data.
```{r}
percentmiss=function(x){sum(is.na(x)/length(x))*100}
```


####To check for missing data by columns
```{r}
apply(VHS12_2,2,percentmiss)
```
####To check for missing data by row
```{r}
missing=apply(VHS12_2, 1,percentmiss)
table(missing)
```
####To exclude participants who are missingn too much data.
```{r}
replacepeople=subset(VHS12_2,missing<=5)
```



####Make sure that the columns are not missing too much data.
```{r}
apply(VHS12_2, 2, percentmiss)
```


#####Base on an analysis of the columns it appears that the data is missing completely at random and we proceed with replacing the data using the package mice.
```{r}
require(mice)
tempnomiss = mice(replacepeople)
nomiss = complete (tempnomiss, 1)
summary(nomiss)
```
###To lookk at data within missing replaced.
```{r}
View(nomiss)
```
####To screen for multivariate outliers.
####To screen for multivariate outliers in the data set nomiss we will use mahalanobis distance statistic.
```{r}
mahal = mahalanobis(nomiss[-c(1)],
                    colMeans(nomiss[-c(1)]),
                    cov(nomiss[-c(1)]))
cutoff = qchisq(0.999, ncol(nomiss[-c(1)])) #####generates cutoff score
ncol(nomiss[-c(1)]) #####determines df
table(mahal<cutoff)
```

###To exelucde the 8 outliers from the analysis.
```{r}
noout = subset(nomiss, mahal<cutoff)
summary(noout)
```





###Multivariate assumption set up.
```{r}
library(tidyverse)
set.seed(1234)
random = rchisq(nrow(noout[-c(1)]),7)
fake = lm(random ~.,data=noout[-c(1)])###Predict random errors which are randomly distribued
standardized = rstudent(fake) ###Standarized residuals.
fitted = scale(fake$fitted.values) ###To scale the values
```
####To test for linearity.
```{r}
qqnorm(standardized)
abline(0,1)
```
####Based on  qq plot we have linearity.
####To test for normality.
```{r}
hist(standardized)
```
####Our variables are linear so we procede to test homogenity of vairance.
####Homogenity of Variance.
```{r}
plot(fitted, standardized)
abline(0,0)
abline(v=0)
```
####To compute a new variable of F0-CV
```{r}
require(dplyr)
noout <- mutate(noout, FOCV=F0_SD/F0)
View(noout)
```

###Lets run the model.
####Model 9
###Do F0 apparent VTL and absolute jitter predict listners health ratings of the speaker.
```{r}
options(scipen = 9999)
M9 = lm(Listeners_Overall_Health_Rating~F0+apparent_VTL_Kalashikova +FOCV+Mean_HNR , data = noout)
summary(M9)
plot(M9)
```
####Lets compute the standardized regression coefficients.
####F0
```{R}
pooledSDF0= sd(noout$F0)/sd(noout$Listeners_Overall_Health_Rating)
pooledSDF0*-0.006313
```
###apparent VTL
```{r}
pooledVTL = sd(noout$apparent_VTL_Kalashikova)/sd(noout$Listeners_Overall_Health_Rating)
pooledVTL* -0.042356
```

####F0-CV
```{r}
pooledSDFOCV= sd(noout$FOCV)/sd(noout$Listeners_Overall_Health_Rating)
pooledSDFOCV*0.506664 
```
####HNR
```{r}
pooledSDMean_HNR= sd(noout$Mean_HNR)/sd(noout$Listeners_Overall_Health_Rating)
pooledSDMean_HNR*-0.40587
```

###Lets run a  model in which speaKers current health and speakers disease resistance.
###Does current health predict F0
```{r}
options(scipen = 9999)
M10= lm(F0~Speakers_Health_Perception_Current_Health_mean, data = noout)
summary(M10)
plot(M10)
```


####F0 standardized coefficient
```{r}
pooledSDSpeakers_Health_Perception_Current_Health_mean= sd(noout$Speakers_Health_Perception_Current_Health_mean)/sd(noout$F0)
pooledSDSpeakers_Health_Perception_Current_Health_mean*-0.845 
```



### Does disease resistance predict F0
```{r}
options(scipen = 9999)
M11= lm(F0~Speakers_Health_Perception_Resistence_mean, data = noout)
summary(M11)
plot(M11)
```
####F0
```{r}
pooledSDSpeakers_Health_Perception_Resistence_mean= sd(noout$Speakers_Health_Perception_Resistence_mean)/sd(noout$F0)
pooledSDSpeakers_Health_Perception_Resistence_mean*-3.608
```












###Lets run a  model in which speaKers current health and speakers disease resistance.
###Does current health predict apparent VTL
```{r}
options(scipen = 9999)
M12= lm(apparent_VTL_Kalashikova~Speakers_Health_Perception_Current_Health_mean, data = noout)
summary(M12)
plot(M12)
```


####apparent VTL
```{r}
pooledSDSpeakers_Health_Perception_Current_Health_mean= sd(noout$Speakers_Health_Perception_Current_Health_mean)/sd(noout$apparent_VTL_Kalashikova)
pooledSDSpeakers_Health_Perception_Current_Health_mean*0.1896 
```



###Does disease resistance apparent VTL.
```{r}
options(scipen = 9999)
M13= lm(apparent_VTL_Kalashikova~Speakers_Health_Perception_Resistence_mean, data = noout)
summary(M13)
plot(M13)
```
####apparent VTL
```{r}
pooledSDSpeakers_Health_Perception_Resistence_mean= sd(noout$Speakers_Health_Perception_Resistence_mean)/sd(noout$apparent_VTL_Kalashikova)
pooledSDSpeakers_Health_Perception_Resistence_mean*0.1352  
```




###Lets run a  model in which speaKers current health and speakers disease resistance.
###Does current health predict FOCV?
```{r}
options(scipen = 9999)
M14 = lm(FOCV~Speakers_Health_Perception_Current_Health_mean, data = noout)
summary(M14)
plot(M14)
```
####F0-CV
```{r}
pooledSDSpeakers_Health_Perception_Current_Health_mean= sd(noout$Speakers_Health_Perception_Current_Health_mean)/sd(noout$FOCV)
pooledSDSpeakers_Health_Perception_Current_Health_mean*-0.02038   
```

###Does disease resistance predict FOCV?
```{r}
options(scipen = 9999)
M15= lm(FOCV~Speakers_Health_Perception_Resistence_mean, data = noout)
summary(M15)
plot(M15)
```
####F0-CV
```{r}
pooledSDSpeakers_Health_Perception_Resistence_mean= sd(noout$Speakers_Health_Perception_Resistence_mean)/sd(noout$FOCV)
pooledSDSpeakers_Health_Perception_Resistence_mean*-0.002484 
```










###Lets run a  model in which speaKers current health and speakers disease resistance.
###Does current health predict HNR
```{r}
options(scipen = 9999)
M16= lm(Mean_HNR~Speakers_Health_Perception_Current_Health_mean, data = noout)
summary(M16)
plot(M16)
```


####HNR
```{r}
pooledSDSpeakers_Health_Perception_Current_Health_mean = sd(noout$Speakers_Health_Perception_Current_Health_mean)/sd(noout$Mean_HNR)
pooledSDSpeakers_Health_Perception_Current_Health_mean*-0.006597  
```



###Does disease resistance predict HNR.
```{r}
options(scipen = 9999)
M17 = lm(Mean_HNR~Speakers_Health_Perception_Resistence_mean, data = noout)
summary(M17)
plot(M17)
```
####HNR
```{r}
pooledSDSpeakers_Health_Perception_Resistence_mean= sd(noout$Speakers_Health_Perception_Resistence_mean)/sd(noout$Mean_HNR)
pooledSDSpeakers_Health_Perception_Resistence_mean*0.02152 
```



##Does speakers current health and disease resistances ratings predict listeners' current health.
```{r}
options(scipen = 9999)
M18 = lm(Listeners_Overall_Health_Rating~Speakers_Health_Perception_Current_Health_mean+Speakers_Health_Perception_Resistence_mean, data = noout)
summary(M18)
plot(M18)
```


####Listeners Overall Health Rating
```{r}
pooledSDListeners_Overall_Health_Rating = sd(noout$Speakers_Health_Perception_Current_Health_mean)/sd(noout$Listeners_Overall_Health_Rating)
pooledSDListeners_Overall_Health_Rating* 0.06465
```


####Listeners Overall Health Rating
```{r}
pooledSDSpeakers_Health_Perception_Resistence_mean  = sd(noout$Speakers_Health_Perception_Resistence_mean )/sd(noout$Listeners_Overall_Health_Rating)
pooledSDSpeakers_Health_Perception_Resistence_mean* -0.06726
```