---
title: "F0 and VTL and attractivensss ratings"
author: "Graham Albert"
date: "June 9, 2019"
output: html_document
---


###To load required packarges
```{r}
require(curl) 
```
######loading data
#####for more advanced rotation.
```{r}
require(dplyr)
```
####for data manipulation.
```{r}
require(yaml)
require(stringi)
```
####for correlation plot depiction.
```{r}
require(gplots)
require(ggplot2)
require(gridExtra)
require(moments)
```

###To load packages for mixed effects models.
```{r}
require(lme4)
require(AICcmodavg)
require(MuMIn)
require(r2glmm)
```
####Packages for mixed effects models.
```{r}
require(RColorBrewer) # needed for some extra colours in one of the graphs
require(lmerTest)# to get p-value estimations that are not part of the standard lme4 packages
```


####To load my data set for the mating motivation scale into the  R work space.
```{r}
f <- curl("https://raw.githubusercontent.com/GrahamAlbert/Voice_Health_Revised/master/Study_3_Female_Attractiveness_Ratings_Long.csv")
VHS3AR<- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(VHS3AR)
```

####To determine variable names of the data set.
```{r}
names(VHS3AR)[1]<-"ID"
names(VHS3AR)

```

####Lets obtain some summary statistics.
```{r}
summary(VHS3AR)
dim(VHS3AR)
View(VHS3AR)
```

####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####These are: ID, participant sex, and speaker ID.
####The fixed effects in this analysis will be  health status.
```{r}
require(dplyr)
VHS3AR_factored = mutate(VHS3AR,ID = as.factor(VHS3AR$ID),ParticipantSex  = as.factor(VHS3AR$ParticipantSex), Manipulation_Type = as.factor(VHS3AR$Manipulation_Type), SPEAKER_ID = as.factor(VHS3AR$SPEAKER_ID))
View(VHS3AR_factored)
```

####Lets determine if we effectively factors the variables of interested.
###We will determine the number of levels for each factor.
```{r}
nlevels(VHS3AR_factored$ID)
nlevels(VHS3AR_factored$ParticipantSex)
nlevels(VHS3AR_factored$Manipulation_Type)
nlevels(VHS3AR_factored$SPEAKER_ID)
```

####Lets look at the distribution of our dependents variables by plotting histrograms
```{r}
require(psych)
hist(VHS3AR_factored$Long_Term_Attractive_F0)
hist(VHS3AR_factored$Long_Term_Attractive_VTL)
hist(VHS3AR_factored$Short_Term_Attractive_F0)
hist(VHS3AR_factored$Short_Term_Attractive_VTL)
describe(VHS3AR_factored[c(5:8)])
```


####To recode recall and encoding so that the reference category changes.
```{R}
VHS3AR_factored$Manipulation_Type = factor(VHS3AR_factored$Manipulation_Type,
                             levels = c(0,1),
                             labels = c("Masculinized", "Feminized"))
table(VHS3AR_factored$Manipulation_Type)
VHS3AR_factored$Manipulation_Type <- relevel(VHS3AR_factored$Manipulation_Type, ref = "Feminized")
```

####Lets save this data.
```{r}
VHS3AR_Master= VHS3AR_factored
summary(VHS3AR_Master)
write.csv(VHS3AR_Master,"C:\\Users\\graha\\Documents\\Github\\Voice_Health_Revised\\VHS3AR_Master", row.names = FALSE)
```
####The dependent variable is long-term attractiveness.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is FO manipulation

```{r}
require(lme4)
LTAFO <- lmer(Long_Term_Attractive_F0~Manipulation_Type+(1|ID)+(1|SPEAKER_ID),REML=FALSE,
           data=VHS3AR_Master)
summary(LTAFO)
```

###To compute adjusted R squared.
```{r}
require(MuMIn)
r.squaredGLMM(LTAFO)
```
####Let's check our multiple regression assumption set for model.
####First, we can check for homoscedasticity . 
```{r}
plot(fitted(LTAFO), resid(LTAFO, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(LTAFO)) 
qqline(resid(LTAFO), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(LTAFO)
confint(LTAFO)
```



####Let's generate the AIC for the 8 models.
```{r}
require(AICcmodavg)
print(aictab(list(LTAFO), c("LTAFO"), LL = FALSE))
```






####The dependent variable is long-term attractiveness.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is VTL manipulation


```{r}
require(lme4)
LTAVTL <- lmer(Long_Term_Attractive_VTL~Manipulation_Type+(1|ID)+(1|SPEAKER_ID), REML=FALSE,
           data=VHS3AR_Master)
summary(LTAVTL)
```

###To compute adjusted R-squared.
```{r}
require(MuMIn)
r.squaredGLMM(LTAVTL)
```
####Let's check our multiple regression assumption set for model.
####First, we can check for homoscedasticity . 
```{r}
plot(fitted(LTAVTL), resid(LTAVTL, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(LTAVTL)) 
qqline(resid(LTAVTL), col = "red")
```

###To generate the fixed effects table for the models .
```{r}
fixef(LTAVTL)
confint(LTAVTL)
```



####Let's generate the AIC for the 8 models.
```{r}
require(AICcmodavg)
print(aictab(list(LTAVTL), c("LTAVTL"), LL = FALSE))
```



####The dependent variable is short-term attractiveness.


####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
####The random effects for the mixed effects listeners' ID, and speaker ID.
####The fixed effects in this analysis is FO manipulation

```{r}
require(lme4)
STAFO <- lmer(Short_Term_Attractive_F0~Manipulation_Type+(1|ID)+(1|SPEAKER_ID),REML=FALSE,
           data=VHS3AR_Master)
summary(STAFO)
```


###To compute adjusted R squared.
```{r}
require(MuMIn)
r.squaredGLMM(STAFO)
```
####Let's check our multiple regression assumption set for models.
####First, we can check for homoscedasticity . 
```{r}
plot(fitted(STAFO), resid(STAFO, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(STAFO)) 
qqline(resid(STAFO), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(STAFO)
confint(STAFO)
```



####Let's generate the AIC for the 8 models.
```{r}
require(AICcmodavg)
print(aictab(list(STAFO), c("STAFO"), LL = FALSE))
```











###Our dependent variable will be short term attractiveness ratings assigned to the voices with the VTL manipulation

#Now lets add the categorical fixed of health status (healthy/unhealth).
```{r}
require(lme4)
STAVTL <- lmer(Short_Term_Attractive_VTL~Manipulation_Type+(1|ID)+(1|SPEAKER_ID),REML=FALSE,
           data=VHS3AR_Master)
summary(STAVTL)
```

###To compute adjusted R squared.
```{r}
require(MuMIn)
r.squaredGLMM(STAVTL)
```
####Let's check our multiple regression assumption set for model 10.
####First, we can check for homoscedasticity by comparing residuals to the fitted items. 
```{r}
plot(fitted(STAVTL), resid(STAVTL, type = "pearson"))
abline(0,0, col="red")
```
####We can also use a QQ-plot to check for normality of residuals. 
```{r}
qqnorm(resid(STAVTL)) 
qqline(resid(STAVTL), col = "red")

```

###To generate the fixed effects table for the models .
```{r}
fixef(STAVTL)
confint(STAVTL)
```



####Let's generate the AIC for the 8 models.
```{r}
require(AICcmodavg)
print(aictab(list(STAVTL), c("STAVTL"), LL = FALSE))
```





